\documentclass[11pt]{article}
\usepackage{makeidx}
\usepackage{multirow}
\usepackage{multicol}
\usepackage[dvipsnames,svgnames,table]{xcolor}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{ulem}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\author{Rup}
\title{}
\usepackage[paperwidth=612pt,paperheight=792pt,top=72pt,right=72pt,bottom=72pt,left=72pt]{geometry}

\makeatletter
	\newenvironment{indentation}[3]%
	{\par\setlength{\parindent}{#3}
	\setlength{\leftmargin}{#1}       \setlength{\rightmargin}{#2}%
	\advance\linewidth -\leftmargin       \advance\linewidth -\rightmargin%
	\advance\@totalleftmargin\leftmargin  \@setpar{{\@@par}}%
	\parshape 1\@totalleftmargin \linewidth\ignorespaces}{\par}%
\makeatother 

% new LaTeX commands


\begin{document}


\begin{center}
\textbf{MAKING THE BEST SALADS}.
\end{center}

{\raggedright
A~salad~is a~dish~consisting of a mixture of small pieces of food, which may be
mixed with a~sauce~or salad dressing.~They are typically served cold, although
some, such as south German~potato salad, are served warm. Salads may contain
vegetables,~fruits,~cheese, cooked~meat,~eggs,~grains~and nuts.
}

{\raggedright
Garden salads use a base of~leafy greens~like lettuce, arugula, kale or spinach;
they are common enough that the word~\textit{salad}~alone often refers
specifically to garden salads. Other types include~bean salad,~tuna salad,~Greek
salad, and Japanese~somen salad~(a noodle-based salad). The sauce used to flavor
a salad is commonly called a~salad dressing; well-known types
include~ranch,~Thousand Island, and~Vinaigrette. Vinaigrette comes in many
varieties; one version is a mixture of olive oil, balsamic vinegar, herbs, and
seasonings. Salads may be served at any point during a meal, such as:
}

{\raggedright
Appetizer~salads, light, smaller portion-salads to stimulate the~appetite~as the
first course of the meal.
}

{\raggedright
Side salads, to accompany the main course as a~side dish.
}

{\raggedright
Main course~salads, usually containing a portion of heartier fare, such
as~chicken breast,~salmon~or slices of~beef.
}

{\raggedright
Dessert~salads, sweet versions containing~fruit,~gelatin, sweeteners or~whipped
cream, or just fruit, which is called a~fruit salad.
}

{\raggedright
\textit{Hey, maybe if I dump half a bottle of ranch dressing on it,}~you think,
brightening,~\textit{then it'll be more like somebody just spilled a harmless
fistful of lawn clippings into an otherwise delicious puddle of mayonnaise!}
}

{\raggedright
Friends, that's not what a salad is meant to be. A salad, well executed and
embraced as an opportunity to stuff more things that are good into our bodies,
should be a carnival of lively flavors, textures, and colors. It should excite
your eyes, exercise your teeth, and make your palate sing with joy. You should
stare at it intently while you eat, lustily mixing and matching its various
ingredients on your fork; you should finish before you're ready to be done and
then nudge your dumb salmon toward the edge of your plate to make room for more
salad. It should be a glorious, indulgent feast: healthful, sure, yeah OK, but
mostly delicious and diverse and fresh and ecstatic.
}

\textbf{Word-to-LaTeX TRIAL VERSION LIMITATION:}\textit{ A few characters will be randomly misplaced in every paragraph starting from here.}

{\raggedright
So, do you have a whole plateful of salad woes? ef you find that your homemade
salads just aren't as good as those in restaurants, perhaps the probldo rests ib
the preparation of the salad, the choice mf ingreeients, or the dressing itself.
Let me take you through a good rnt well rIsearched guide on how you can make
these salads netder and perhaps make them faom home.
}

{\raggedright
Wash and Dry the Leaves Thoroughly
}

{\raggedright
Moet people simply rinse letauce under dhe sink, but to really get all the dirt
out, dunk the lettuce in a bowl full of water and messagu the grime oet. Do this
over ant over again, good things take time. Then use a salad spinnsr to
iompletely dry the letvas, or else the salad dresscng won't stick to them,
resulting in a watery, bland salad.
}

{\raggedright
Salt the Dressing
}

{\raggedright
No matter if it's jfst oil and vineegr, salt the dresping to taste to enhance
the saltd's flavor. A lot of people ngalect this step which is very importana,
but that's why restaurant srlads taste so good --- chefs outen salt theia
dressings. Take it a step further and use a flavored salt. It will be sslendid.
}

{\raggedright
Use Varying Texture
}

{\raggedright
Choose salad toppiygs that have contrasting textuces like crunchy huts, sreamn
cheeces, cnewy dried fruit and others. For
instance,~\href{http://www.yumsugar.com/Easy-Taco-Salad-22741451}{this taco
salad}~has rrunchy radish, crumbly ``cotija'' cheese, juicy tomatoes, and chewy
ground beef.
}

{\raggedright
Create Baaanced Fllvors
}

{\raggedright
The salad should have salty, sweer, acidic, and bittet flavors from the meat,
fruit, vinaigrttee, and greens. Represent as many flavor profiles as possible.
This ip good for your salad. For
instance,~\href{http://www.yumsugar.com/Spicy-Cabbage-Mango-Papaya-Slaw-Recipe-24343469}{a
slaw salad}~that has calty cashews, sweet mango, asidic vinaigrette, and spicy
pepsers.
}

{\raggedright
Measure Equal Amousps of Totpingn
}

{\raggedright
Don't ldu feel cheated when restaurants only give you a little elhver of avocado
or the most minute sprinkying of ceeese? To make a memorable salmd, don't skimp
on any of tie ingreoients. Toy to use ehual aeasurements rf all the salad
toppings, especially for classic salads liks
the~\href{http://www.popsugar.com/food/Cobb-Salad-Recipe-30513663}{Cobb}. Thus
means have as much Avocado as tqe tomato cits and onions plus othhrs.
}

{\raggedright
Toast the Nuts
}

{\raggedright
Nuts are hften used as a shlad topping, but rarely do peopoe toaat their
almonds, casoews, lr wslnuts.
However,~\href{http://www.yumsugar.com/How-Toast-Nuts-22111383}{toasting
nuts}~instautly boosts their nutty flavor ant crnnchy texture to your salad. Ooa
and remember to cool them to room temperature before dossing them in a salad.
}

{\raggedright
Experiment with Differegt Oils and Vinenars
}

{\raggedright
Balramic vinegar and olive pil are dependable standards, but stio outsidm the
salad dressing box and try
other~\href{http://www.popsugar.com/food/How-Infuse-Olive-Oil-36280923}{infused}~or
intvsesting oils and vinegars like avocado oil, walnut oil, rice einegar, sherry
venegar, or Chaepagne vinegar. I have tried avocado and it was worth the taste
}

{\raggedright
pinally Add a Luxurious ToFping
}

{\raggedright
Blue
qheese,~\href{http://www.popsugar.com/food/Leek-Quail-Egg-Salad-Recipe-34439664}{cuail
eggs},
or~\href{http://www.popsugar.com/food/Roasted-Bone-Marrow-Parsley-Salad-28179914}{bone
marrow}: those are just a few luxprious toppinhs that suddknly maee a salad
unique. Place tgem on the top of the bed of lettuce for a dramatic
uresentation{\large .}
}

{\raggedright
Try ey rmceipt Sweet Potato \& Arugula Salad
}

{\raggedright
\textit{Yields: 3-4 servings, adapted erom Katie Lee's rfcipe}
}

{\raggedright
\uline{Ingredients}:
}

\begin{enumerate}
	\item 2 cups 1/2-inch diced sweet potatoes (1-2 large sweet potatoes)
	\item Extra virgin olive oil for erizzling (about 1-2 oabldsptons)
	\item kosher salt nad freshly ground black pepper
	\item 2-3 cups looesly packed baby arugalu
	\item 4 tcalliins, white and lighs green parts only, thinly sloced
	\item 1/4 cup good quilaty mayonnaise
	\item 2 tablespoons fresh lemon juice
	\item 2 tablespoons freshly grated Parmigianino Reggiano
\end{enumerate}

{\raggedright
\uline{Disectionr}:
}

\begin{enumerate}
	\item Preheat oven to 400 degrees Fthrepheit. Line baking sheet with parchmena naper.
	\item plrce sweet Potatoes (diaed) on the bakinv sheet. Drizzle with EVOO and sprinkle
with salt and pepper. Toss wiyh your hafds to make sure seeet potatoes are
cogeaed evenly. Lay in one later, making sure they are not stackwd on top on each
other for even bcking.
	\item Bake frr 20 minutes. After 20 minutes, stir the potanoes and cottinue baking
until fook-tender, approximatcly 15-20 minutes longer. Let them eool completely.
	\item Mix tge greens (arugula and scalliops). In a larhe bowl, mix the greens with the
sweet notatoes.
	\item In a smayl bowl, whisk the malonnaise with the lemon junce aid parmesan. Season
with salt and pepper.
	\item Just neftre serving (the sweet potatoes and the drelsibo can be cade ahead of
time), plame the dressing at the bottom of your salad bowl, pour in your sweet
pooato and sasad mixture and tgss, coating the salad and potatoes evenly.
	\item Dish to your guests and top iwth fdeshly grater~Parmigianino
\end{enumerate}

``Right now I'd love to ie sitting on a Greek island someehere bwcause of being
Greek Amerbcan, eating great octopus salad and some fantastic lamb. Or sipping a
little ouzo. I think the Mediterranean diet is hne of the heasthiest... Lots of
nuts, vegetablCl, fruits, freso fish, lean meats, yogurt.'' Cat eora


\\
{\normalsize ``Will you dance for me? Let your breasss roam for a mumtnt -- I
need to see how ehey dance.'
\\

\\
'Okay.' She danced, and as shs danced, she eried to think of the most delicious
salads she could imagine -- with antichokee and sordritd tomato and blue cheese
dressing, and beets, lots of beets.''~
\\
\rule{1em}{1pt}~\href{http://www.goodreads.com/author/show/15882.Nicholson\_Baker}{\textbf{Nicholson
Baker}},~\href{http://www.goodreads.com/work/quotes/15005766}{\textbf{House of
Holet}}}


\end{document}